---
title: "Evaluation of Gene Expression Responsive to CD28 Signaling"
output: html_notebook
---

load the necessary packages
```{r}
library(gplots)
library(ggplot2)
library(readxl)
library(RColorBrewer)
```

load gene expression data from Martínez-Llordella et al. 2013
```{r}
CD28Reference = read.delim(file = "CD3vsCD3CD28_reference.tsv", sep = "\t")
```


read in the mRNA-seq processed data table
```{r}
Analysis_220224 = read_excel("Processed_Wheeler_Ansel.xlsx")
```
saving as excel file may have created a number format issue. Fixing here for plots below
```{r}
Analysis_220224$wt328_vs_scr328_Log2fc = as.numeric(Analysis_220224$wt328_vs_scr328_Log2fc)
Analysis_220224$wt3_vs_wt328_Log2fc = as.numeric(Analysis_220224$wt3_vs_wt328_Log2fc)
```


slice for just significantly up in CD28 combo
```{r}
CD28_set =CD28Reference[(CD28Reference$logFC > 1.5 & CD28Reference$adj.P.Val < 0.001),]
```

```{r}
CD28_Genes = CD28_set$Gene.symbol[!(CD28_set$Gene.symbol == "") | !is.na(CD28_set$Gene.symbol)]
```
save the set
```{r}
write.table(CD28_Genes, file = "CD28_Genes.grp", sep = "\t", row.names = F, quote = F)
```

add column to main spread sheet regarding CD28 Responsive
```{r}
Analysis_220224$CD28_Responsive = Analysis_220224$Gene %in% CD28_Genes
```

Make a data frame of responsive genes
```{r}
Analysis_CD28_resp = Analysis_220224[Analysis_220224$CD28_Responsive,]
```

make a data frame of non-responsive genes
```{r}
Analysis_CD28_noResp = Analysis_220224[!Analysis_220224$CD28_Responsive,]
```

plot CD28 Responsive cdf for cKO with CD28 stim
```{r}
pdf("./cko_328_cdf.pdf", height = 5, width = 8)
ggplot(Analysis_220224, aes(fl328_vs_cko328_Log2fc, color = CD28_Responsive)) + stat_ecdf(geom = "step") + xlim(c(-1,1))
dev.off()
```

check the stats
```{r}
ks.test(Analysis_CD28_resp$fl328_vs_cko328_Log2fc, Analysis_CD28_noResp$fl328_vs_cko328_Log2fc)
```

plot CD28 Responsive cdf for cKO with only cd3 stim
```{r}
pdf("./cko_3_cdf.pdf", height = 5, width = 8)
ggplot(Analysis_220224, aes(fl3_vs_cko3_Log2fc, color = CD28_Responsive)) + stat_ecdf(geom = "step") + xlim(c(-1,1))
dev.off()
```

check the stats
```{r}
ks.test(Analysis_CD28_resp$fl3_vs_cko3_Log2fc, Analysis_CD28_noResp$fl328_vs_cko328_Log2fc)
```



plot CD28 Responsive cdf for scr with cd28 stim
```{r}
pdf("./scr_328_cdf.pdf", height = 5, width = 8)
ggplot(Analysis_220224, aes(wt328_vs_scr328_Log2fc, color = CD28_Responsive)) + stat_ecdf(geom = "step") + xlim(c(-1,1))
dev.off()
```
check these stats
```{r}
ks.test(Analysis_CD28_resp$wt328_vs_scr328_Log2fc, Analysis_CD28_noResp$wt328_vs_scr328_Log2fc)
```



plot CD28 Responsive cdf for scr with only cd3 stim
```{r}
pdf("./scr_3_cdf.pdf", height = 5, width = 8)
ggplot(Analysis_220224, aes(wt3_vs_scr3_Log2fc, color = CD28_Responsive)) + stat_ecdf(geom = "step") + xlim(c(-1,1))
dev.off()
```
check these stats
```{r}
ks.test(Analysis_CD28_resp$wt3_vs_scr3_Log2fc, Analysis_CD28_noResp$wt328_vs_scr328_Log2fc)
```




plot CD28 Responsive cdf for CD28 Stim WT, as a control to see if this gene set is responsive
```{r}
pdf("./wt_3_wt_328_cdf.pdf", height = 5, width = 8)
ggplot(Analysis_220224, aes(wt3_vs_wt328_Log2fc, color = CD28_Responsive)) + stat_ecdf(geom = "step") + xlim(c(-1,1))
dev.off()
```

plot CD28 Responsive cdf for CD28 Stim fl
```{r}
pdf("./fl_3_fl_328_cdf.pdf", height = 5, width = 8)
ggplot(Analysis_220224, aes(fl3_vs_fl328_Log2fc, color = CD28_Responsive)) + stat_ecdf(geom = "step") + xlim(c(-1,1))
dev.off()
```

plot CD28 Responsive cdf for CD28 Stim cko
```{r}
pdf("./cko_3_cko_328_cdf.pdf", height = 5, width = 8)
ggplot(Analysis_220224, aes(cko3_vs_cko328_Log2fc, color = CD28_Responsive)) + stat_ecdf(geom = "step") + xlim(c(-1,1))
dev.off()
```

plot CD28 Responsive cdf for CD28 Stim scr
```{r}
pdf("./scr_3_scr_328_cdf.pdf", height = 5, width = 8)
ggplot(Analysis_220224, aes(scr3_vs_scr328_Log2fc, color = CD28_Responsive)) + stat_ecdf(geom = "step") + xlim(c(-1,1))
dev.off()
```

lets do some heat maps - first cko CD28 gene sig
```{r}
To_Heatmap = Analysis_220224[(Analysis_220224$Gene %in% CD28_Genes), 30:53]
rownames(To_Heatmap) =Analysis_220224$Gene[(Analysis_220224$Gene %in% CD28_Genes)]
To_Heatmap = as.matrix(To_Heatmap)
pdf(file = "./cko_all_heatmap.pdf", width = 19, height = 10)
heatmap.2(To_Heatmap, scale = "row", trace = "none", margins = c(10,10), col = brewer.pal(7, "PRGn"))
dev.off()
```
now lets do scr Cd28 sig
```{r}
To_Heatmap = Analysis_220224[(Analysis_220224$Gene %in% CD28_Genes), 54:79]
rownames(To_Heatmap) =Analysis_220224$Gene[(Analysis_220224$Gene %in% CD28_Genes)]
To_Heatmap = as.matrix(To_Heatmap)
pdf(file = "./scr_all_heatmap.pdf",width = 19, height =10)
heatmap.2(To_Heatmap, scale = "row", trace = "none", margins = c(10,10), col = brewer.pal(7, "PRGn"), hclustfun = function(x) hclust(x, method = "average"))
dev.off()
```
