---
title: "RNA seq Results Reprocessing"
output: html_notebook
---

load necessary packages
```{r}
library(ggfortify)
library(VennDiagram)
library(ggplot2)
library(umap)
library(writexl)
```


load all genes data set
```{r}
All_genes = read.csv(file = "All_genes.1056_Ansel.csv")
```

remove genes with <100 avg in norm counts
```{r}
m = dim(All_genes)
for(i in 1:m[1]){
  All_genes$Robust_Expression[i] = (mean(as.matrix(All_genes[i,30:79]))>100)
  
}

Robust_genes = All_genes[All_genes$Robust_Expression,]
```

Add Pairwise Comparisons for the following relevant comparisons using norm values
columns of samples
wt 3 74:79
wt 3 28 68:73
scr 3 61:67
scr 3 28 54:60

fl 3 48:53
fl 3 28 42:47
cko 3 36:41
cko 3 28 30:35
-----------------
WT 3 vs SCR 3
WT 3 vs WT 3 28
WT 3 28 vs scr 3 28
scr 3 vs scr 3 28

fl 3 vs cko 3
fl 3 vs fl 3 28
fl 3 28 vs cko 3 28
cko 3 vs cko 3 28
```{r}
Analysis_220224 = Robust_genes
n = dim(Analysis_220224)

for(i in 1:n[1]){
  Analysis_220224$wt3_vs_scr3_fc[i] = mean(as.matrix(Analysis_220224[i,74:79]))/mean(as.matrix(Analysis_220224[i,61:67]))
  Analysis_220224$wt3_vs_scr3_RawP[i] = t.test(as.matrix(Robust_genes[i,74:79]),as.matrix(Robust_genes[i,61:67]))[3]
  
  Analysis_220224$wt3_vs_wt328_fc[i] = mean(as.matrix(Analysis_220224[i,74:79]))/mean(as.matrix(Analysis_220224[i,68:73]))
  Analysis_220224$wt3_vs_wt328_RawP[i] = t.test(as.matrix(Robust_genes[i,74:79]),as.matrix(Robust_genes[i,68:73]))[3]
  
  Analysis_220224$wt328_vs_scr328_fc[i] = mean(as.matrix(Analysis_220224[i,68:73]))/mean(as.matrix(Analysis_220224[i,54:60]))
  Analysis_220224$wt328_vs_scr328_RawP[i] = t.test(as.matrix(Robust_genes[i,68:73]),as.matrix(Robust_genes[i,54:60]))[3]
  
  Analysis_220224$scr3_vs_scr328_fc[i] = mean(as.matrix(Analysis_220224[i,61:67]))/mean(as.matrix(Analysis_220224[i,54:60]))
  Analysis_220224$scr3_vs_scr328_RawP[i] = t.test(as.matrix(Robust_genes[i,61:67]),as.matrix(Robust_genes[i,54:60]))[3]
  
  Analysis_220224$fl3_vs_cko3_fc[i] = mean(as.matrix(Analysis_220224[i,48:53]))/mean(as.matrix(Analysis_220224[i,36:41]))
  Analysis_220224$fl3_vs_cko3_RawP[i] = t.test(as.matrix(Robust_genes[i,48:53]),as.matrix(Robust_genes[i,36:41]))[3]
  
  Analysis_220224$fl3_vs_fl328_fc[i] = mean(as.matrix(Analysis_220224[i,48:53]))/mean(as.matrix(Analysis_220224[i,42:47]))
  Analysis_220224$fl3_vs_fl328_RawP[i] = t.test(as.matrix(Robust_genes[i,48:53]),as.matrix(Robust_genes[i,42:47]))[3]
  
  Analysis_220224$fl328_vs_cko328_fc[i] = mean(as.matrix(Analysis_220224[i,42:47]))/mean(as.matrix(Analysis_220224[i,30:35]))
  Analysis_220224$fl328_vs_cko328_RawP[i] = t.test(as.matrix(Robust_genes[i,42:47]),as.matrix(Robust_genes[i,30:35]))[3]
  
  Analysis_220224$cko3_vs_cko328_fc[i] = mean(as.matrix(Analysis_220224[i,36:41]))/mean(as.matrix(Analysis_220224[i,30:35]))
  Analysis_220224$cko3_vs_cko328_RawP[i] = t.test(as.matrix(Robust_genes[i,36:41]),as.matrix(Robust_genes[i,30:35]))[3]

  
  
}



```

remove na genes
```{r}
Analysis_220224 = Analysis_220224[!(is.na(Analysis_220224$Gene)),]
```


add in log2fc for above comparisons
```{r}
Analysis_220224$wt3_vs_scr3_Log2fc = log2(Analysis_220224$wt3_vs_scr3_fc)
Analysis_220224$wt3_vs_wt328_Log2fc = log2(Analysis_220224$wt3_vs_wt328_fc)
Analysis_220224$wt328_vs_scr328_Log2fc = log2(Analysis_220224$wt328_vs_scr328_fc)
Analysis_220224$scr3_vs_scr328_Log2fc = log2(Analysis_220224$scr3_vs_scr328_fc)

Analysis_220224$fl3_vs_cko3_Log2fc = log2(Analysis_220224$fl3_vs_cko3_fc)
Analysis_220224$fl3_vs_fl328_Log2fc = log2(Analysis_220224$fl3_vs_fl328_fc)
Analysis_220224$fl328_vs_cko328_Log2fc = log2(Analysis_220224$fl328_vs_cko328_fc)
Analysis_220224$cko3_vs_cko328_Log2fc = log2(Analysis_220224$cko3_vs_cko328_fc)
```

Adjust P-Values to FDR 
```{r}
Analysis_220224$wt3_vs_scr3_FDR = p.adjust(as.numeric(Analysis_220224$wt3_vs_scr3_RawP), method = "fdr")
Analysis_220224$wt3_vs_wt328_FDR = p.adjust(Analysis_220224$wt3_vs_wt328_RawP, method = "fdr")
Analysis_220224$wt328_vs_scr328_FDR = p.adjust(Analysis_220224$wt328_vs_scr328_RawP, method = "fdr")
Analysis_220224$scr3_vs_scr328_FDR = p.adjust(Analysis_220224$scr3_vs_scr328_RawP, method = "fdr")

Analysis_220224$fl3_vs_cko3_FDR = p.adjust(Analysis_220224$fl3_vs_cko3_RawP, method = "fdr")
Analysis_220224$fl3_vs_fl328_FDR = p.adjust(Analysis_220224$fl3_vs_fl328_RawP, method = "fdr")
Analysis_220224$fl328_vs_cko328_FDR = p.adjust(Analysis_220224$fl328_vs_cko328_RawP, method = "fdr")
Analysis_220224$cko3_vs_cko328_FDR = p.adjust(Analysis_220224$cko3_vs_cko328_RawP, method = "fdr")
```

transform P values
```{r}
Analysis_220224$wt3_vs_scr3_NegLogP = -log10(as.numeric(Analysis_220224$wt3_vs_scr3_RawP))
Analysis_220224$wt3_vs_wt328_NegLogP = -log10(as.numeric(Analysis_220224$wt3_vs_wt328_RawP))
Analysis_220224$wt328_vs_scr328_NegLogP = -log10(as.numeric(Analysis_220224$wt328_vs_scr328_RawP))
Analysis_220224$scr3_vs_scr328_NegLogP = -log10(as.numeric(Analysis_220224$scr3_vs_scr328_RawP))

Analysis_220224$fl3_vs_cko3_NegLogP = -log10(as.numeric(Analysis_220224$fl3_vs_cko3_RawP))
Analysis_220224$fl3_vs_fl328_NegLogP = -log10(as.numeric(Analysis_220224$fl3_vs_fl328_RawP))
Analysis_220224$fl328_vs_cko328_NegLogP = -log10(as.numeric(Analysis_220224$fl328_vs_cko328_RawP))
Analysis_220224$cko3_vs_cko328_NegLogP = -log10(as.numeric(Analysis_220224$cko3_vs_cko328_RawP))
```

save the processed file
```{r}
writexl::write_xlsx(Analysis_220224, path = "Processed_Wheeler_Ansel.xlsx")
```


